%-------------------------------------------------------------------------------
%	EXPERIENCE TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Backend Engineer} % Job title
    {Stash} % Organization
    {New York, NY} % Location
    {June 2018 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected and Dockerized a load testing framework for a new backend service using the Python Locust framework.}
        \item {Integrated CircleCI into a new backend services code repository, created Terraform and AWS resources for this service.}
      \end{cvitems}
    }
\vspace{5mm}
%---------------------------------------------------------
  \cventry
    {Software Engineer II} % Job title
    {Rent the Runway} % Organization
    {New York, NY} % Location
    {Apr. 2017 - Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead engineer on custom Dropwizard (Java) shipping system. Includes address validation via UPS Connectship, custom label generating, and package rating via UPS, FedEx, \\Doorman, Deliv, TForce, Breakaway with a deterministic shipping method outcome.}
        \item {Implemented inventory tracking and resolution system used by warehouse staff to trace \$1M+/yr in lost inventory.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer I} % Job title
    {} % Organization
    {} % Location
    {Dec. 2015 - Apr. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Delivered Unit Priority Blue, an algorithmically complex two-person project with Chief \\Analytics Officer visibility, which led to an automatic reduction in average unfulfillable order volume by roughly 10\%, and savings of \$1.25 in COGS per shipment.}
        \item {Implemented Ansible automation software into proprietary Ruby software being migrated to pristine private cloud servers, enabling the shutting down of public cloud servers and savings of roughly \$20,800/mo.}
        \item {Integrated Doorman (a same day courier service) into proprietary shipping system. Also improved the system's outbound carrier decision flow logic, resulting in improved customer satisfaction and an annualized \$1.50 cost reduction per courier shipment.}
        \item {Cross-team collaborated to integrate enterprise warehouse automation software (provided by Reddwerks) with proprietary warehouse order fulfillment software via AMQP messaging. Project scope had VP, SVP and Chief Logistics Officer visibility.}
      \end{cvitems}
    }

%---------------------------------------------------------
\vspace{5mm}
  \cventry
    {Software Engineering Intern} % Job title
    {IBM} % Organization
    {Littleton, MA} % Location
    {July 2014 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected Java integration test framework across SmartCloud Notes (SCN) platform, which was given to superiors that will continue to develop it. The framework will be used to replace Selenium for back-end testing and drastically reduce the failure rate of 25\% of all test cases that occur on the SmartCloud Notes platform.}
        \item {Designed synchronization of Selenium UI tests to IBM Domino API server-side tests, \\probability calculation using machine learning with CouchDB, and server status checking.}
        \item {Assisted Product Management Team with maintaining consistency between SCN Software Problem Report db, Prioritization db and IBM Connections Ideation group.}
      \end{cvitems}
    }

%---------------------------------------------------------
\vspace{5mm}
  \cventry
    {Software Engineering Intern} % Job title
    {PHT (acquired by ERT Clinical)} % Organization
    {Boston, MA} % Location
    {Jan. 2013 - June 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Generated LogPad medical device testing data by building Python scripts using pre-designed templates.}
        \item {Applied software builds to LogPads/SitePads, tested and validated the software, and \\prepared data summaries.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}