%-------------------------------------------------------------------------------
%	PROJECTS TITLE
%-------------------------------------------------------------------------------
\vspace{10mm}

\cvsection{Technical Projects}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Co-Founder \& Developer} % Job title
    {\href{http://cheddah.herokuapp.com/}{Cheddah}} % Organization
    {} % Location
    {Feb. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deployed Swift 4 app to App Store, and developed a standalone (importable) CocoaPod version of the app. Implements SnapKit pod for Auto Layout constraints management.}
        \item {Deployed Android app to Google Play Store, and developed a standalone Android library (Maven) dependency version of the app using Gradle with Groovy.}
        \item {Deployed Ruby on Rails server app to Heroku. Implemented Coffeescript with jQuery for front-end user interactivity, Sidekiq with Redis for background job processing, PostgreSQL for database modeling, Amazon S3 with Carrierwave for assets management, and Twilio API for SMS text messaging.}
      \end{cvitems}
    }

%---------------------------------------------------------
\vspace{5mm}
  \cventry
    {Co-Founder \& Developer} % Job title
    {GoSlow} % Organization
    {} % Location
    {Feb. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Deployed Ruby on Rails server app to Heroku and implemented PostgreSQL for database modeling.}
        \item {Developing Swift 4 app. Implemented GoogleMaps for iOS (pod) and Google Roads, Distance, and Places APIs for GPS navigation in Nigeria.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}